\documentclass{article}

\usepackage[a4paper,left=2.7cm,right=2.7cm,top=3.5cm,bottom=3.5cm]{geometry}
\usepackage{xcolor}

\title{Coding \\ \large{Hobbies and Interests}}
\author{Administrator Yang}
\date{\today}

\begin{document}

\maketitle
\section{Beginning}
\paragraph{\hspace{2em}Everyone has a variety of hobbies and interests. Some love badminton and enjoy the thrill of smashing a powerful shot; some are passionate about cycling, experiencing speed and excitement on the road; others are devoted to science, eager to explore new knowledge and expand their horizons. As for me, I am deeply passionate about information technology, especially programming.}
\section{History}
\paragraph{\hspace{2em}I was first introduced to programming on September 1, 2023, when I started learning Scratch. Later, in September 2024, during my first IT lab class, I encountered the C++ language. Since then, I’ve learned about loops, if-else conditional statements, generating random numbers, and eventually moved away from \textcolor{gray}{using namespace std}. I also discovered GitHub and, through conversations with AI, was introduced to LaTeX. My first open-source project was a book report written in LaTeX: \textcolor{blue}{https://github.com/gcc-404-NOT-FOUND/Red-Star-over-China.}}
\section{Why do I love}
\paragraph{\hspace{2em}Throughout my learning journey, I’ve adhered to the principle: If I can’t afford it or it’s not available, I’ll make it myself. I often spend at least three hours in one sitting while coding. I truly enjoy the sense of control over how the code runs and the output it produces. Every time I update my code, I feel a great sense of accomplishment. Next, please enjoy a video I edited myself: \textcolor{cyan}{the song \textit{Wasted}, dedicated to everyone who loves programming.}}
\section{Ending}
\paragraph{\hspace{2em}In summary, programming is the only hobby I’ve consistently pursued for over a year. I’m currently learning C++, LaTeX, and Python. If you also enjoy programming, feel free to chat with me! You can also follow my GitHub account: \textcolor{blue}{https://github.com/gcc-404-NOT-FOUND.}}
\begin{center}
\Huge{\LaTeX}\par
\Large{Source Code:\textcolor{blue}{https://github.com/gcc-404-NOT-FOUND/Coding-Lover}}
\end{center}
\end{document}
